An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
more concise
better wording for first part

In this section, we present several {\em tricky} configuration errors
extracted from real-world examples. 
The reason we call them tricky is that
most existing efforts, \eg, learning-based checking
efforts~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors.
On the other hand, we also investigated 
many misconfiguration problems in practice which were caused by 
these tricky configuration errors, \eg, reported by Stack Overflow.

@@

\ennan{Example~4: This should be the singular value error.
We need an example from Stack Overflow to illustrate the 
real-world problem. I guess the buffer size example is fine.}

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A configuration error reported recently made the MySQL
daemon fail to start~\cite{syserror}.
One entry was written as 
{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
format, seemed correct.
However, the problem is that this directory should not 
contain the root directory; the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called a system environment-related configuration error.
Both \app and EnCore can handle misconfigurations concerning system execution.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.

>>>>

In this section, we present several {\em tricky} configuration errors
extracted from real-world examples. 
The reason we call them tricky is that
most existing efforts, \eg, learning-based checking
efforts~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors. We investigated 
many misconfiguration problems in practice which were caused by 
these tricky configuration errors, such as those reported on StackOverflow.

@@

\para{Example~4: Singular Value Errors} 
This should be the singular value error.
We need an example from Stack Overflow to illustrate the 
real-world problem. I guess the buffer size example is fine.}

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A configuration error reported recently made the MySQL
daemon fail to start~\cite{syserror}.
One entry was written as 
{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
format, seemed correct.
However, the problem is that this directory should not 
contain the root directory; the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called a system environment-related configuration error.
Both \app and EnCore can handle misconfigurations concerning system execution.
Furthermore, \app is also able to detect type and syntax errors
in configuration files.
